Convergence rate of MAP estimates \\ for the exponential family

### 2021-10-20 aistats.tex
Move self-concordance definition

The Gaussian log-partition function and entropy are up to constants
\alignn{
	\logpart(\nat) &= \frac{\nat_1^2}{-4\nat_2} - \half \log(-\nat_2) \\
	\conj(\m) &= - \half \log (\mu_2 - \mu_1^2) \; ,
}
where $\nat_1\in\real, \nat_2 <0$ and $\mu_1\in\real, \mu_2>\mu_1^2$.
These functions and their domains they are represented in Figure \TODO{}.

@@

\paragraph{Log-partition is not Self-Concordant}
Let us fix a straight line with $\nat_1 \neq 0$, e.g. $g(\nat_2) := A(\nat_1,\nat_2)$. Then
\alignn{
g'(\nat_2) = \frac{\partial A}{\partial\nat_2}(\nat) 
&= +\frac{\nat_1^2}{4 \nat_2^2} + \frac{1}{2\nat_2} \\
g''(\nat_2) = \frac{\partial^2 A}{(\partial\nat_2)^2}(\nat) 
&= -\frac{\nat_1^2}{2 \nat_2^3} - \frac{1}{2\nat_2^2} 
=  \frac{1}{2\nat_2^2}\paren{\frac{\nat_1^2}{-\nat_2^2} - 1} \\ 
g'''(\nat_2) = \frac{\partial^3 A}{(\partial\nat_2)^3}(\nat) 
&= +\frac{3\nat_1^2}{2 \nat_2^4} + \frac{1}{\nat_2^3}
= \frac{1}{2\nat_2^3}\paren{2 - 3 \frac{\nat_1^2}{- \nat_2^2}}
}
Setting $\nat_2 = - \nat_1^2$ yields $g''(\nat_2) = 0$ and $g'''(\nat_2) \neq 0$, meaning the second derivative cannot dominate the third derivative for any choice of constant. The log-partition is neither self concordant nor pseudo-self-concordant.

>>>>

The Gaussian log-partition function and entropy are, up to constants,
\alignn{
	\logpart(\nat) &= \frac{\nat_1^2}{-4\nat_2} - \half \log(-\nat_2) \\
	\conj(\m) &= - \half \log (\mu_2 - \mu_1^2) \; ,
}
where $\nat_1\in\real, \nat_2 <0$ and $\mu_1\in\real, \mu_2>\mu_1^2$.
These functions and their domains they are represented in Figure \TODO{}.
We provide definitions of self-concordance in \cref{app:self-concordant}.

@@

\paragraph{Log-partition is not Self-Concordant}
Let us fix a straight line with $\nat_1 \neq 0$, e.g. $g(\nat_2) := A(\nat_1,\nat_2)$. Then
\alignn{
g'(\nat_2) = \frac{\partial A}{\partial\nat_2}(\nat) 
&= +\frac{\nat_1^2}{4 \nat_2^2} + \frac{1}{2\nat_2} \\
g''(\nat_2) = \frac{\partial^2 A}{(\partial\nat_2)^2}(\nat) 
&= -\frac{\nat_1^2}{2 \nat_2^3} - \frac{1}{2\nat_2^2} 
=  \frac{1}{2\nat_2^2}\paren{\frac{\nat_1^2}{-\nat_2^2} - 1} \\ 
g'''(\nat_2) = \frac{\partial^3 A}{(\partial\nat_2)^3}(\nat) 
&= +\frac{3\nat_1^2}{2 \nat_2^4} + \frac{1}{\nat_2^3}
= \frac{1}{2\nat_2^3}\paren{2 - 3 \frac{\nat_1^2}{- \nat_2^2}}
}
Setting $\nat_2 = - \nat_1^2$ yields $g''(\nat_2) = 0$ and $g'''(\nat_2) \neq 0$, meaning the second derivative cannot dominate the third derivative for any choice of constant or exponent. The log-partition is neither self concordant nor pseudo-self-concordant.
